Lunar Lander with Deep Reinforcement Learning

### 2019-07-01 project_2/paper/paper.tex
Adding final paper

\author{
Carlos Souza\thanks{Latest Git hash: INCLUDE LATEST GITHASH}\\
%Department of Computer Science\\
Georgia Institute of Technology\\
%São Paulo, SP, Brazil \\
\texttt{souza@gatech.edu} \\
}

@@

    While varying the extensions, we kept all other hyper-parameters frozen.
    We used RMSProp as the optimization algorithm, with $\alpha$ (learning rate) of $0.0001$.
    $\gamma$ (discount factor) was set at $0.99$.
    Replay memory capacity was set to $10,000$ experience tuples, and training was performed using $32$ as mini-batch size.
    The network architecture consists of 2 fully-connected hidden layers with 512 neurons each, both with rectified linear unit (ReLU) activation functions (for dueling network: we added a fully-connected layer as described previously).
    For prioritized replay, we annealed the bias by progressively increasing $\beta$ (exponent in importance-sampling weights) from $0.4$ to $1$.
    As exploration strategy, we decayed $\epsilon$ following $\epsilon(t) = e^{-t/70}$, where $t$ is the current episode, until hitting $0.05$, staying constant at $0.05$ from that point on.

    To reduce the variability given the stochasticity, this experiment was performed 20 times for each variant.

@@

    \paragraph{Experiment 3: Discount factor sensitivity.}
    In this experiment, we investigated the effect of $\gamma$ in the integrated agent's performance.
    We tested all $\gamma \in [0.8, 0.85, 0.9, 0.92, 0.94, 0.96, 0.98, 0.99, 1.0]$.
    As usual, all other hyper-parameters were kept frozen.
    To reduce the variability given the stochasticity, this experiment was performed 5 times for each variant.

    \paragraph{Experiment 4: Evaluation of different exploration strategies.}
    Following, we evaluated the impact of $10$ different $\epsilon$ decay curves.
    We assessed two types of curves: exponential decay functions, $\epsilon(t) = e^{-k t}$; and inverted logistic functions, $\epsilon(t) = 1 / (1 + e^{-k_{1} (t - k_{2})})$.
    Again, all other hyper-parameters were kept frozen.
    To reduce the variability given the stochasticity, this experiment was performed 10 times for each variant.

>>>>

\author{
Carlos Souza\thanks{Latest Git hash: 5b33898a39727cea2d7f0a0872acdd30f9d2a1e5}\\
%Department of Computer Science\\
Georgia Institute of Technology\\
São Paulo, SP, Brazil \\
\texttt{souza@gatech.edu} \\
}

@@

    While varying the extensions, we kept all other hyper-parameters frozen.
    We used RMSProp as the optimization algorithm, with $\alpha$ (learning rate) of $0.0001$.
    $\gamma$ (discount factor) was set at $0.99$.
    Replay memory capacity was set to $10,000$ experience tuples, and training was performed using $32$ as mini-batch size.
    The network architecture consists of 2 fully-connected hidden layers with 512 neurons each, both with rectified linear unit (ReLU) activation functions (for dueling network: we added a fully-connected layer as described previously).
    For prioritized replay, we annealed the bias by progressively increasing $\beta$ (exponent in importance-sampling weights) from $0.4$ to $1$.
    As exploration strategy, we decayed $\epsilon$ following $\epsilon(t) = e^{-t/70}$, where $t$ is the current episode, until hitting $0.05$, staying constant at $0.05$ from that point on.
    To reduce the variance given the stochasticity, this experiment was performed 20 times for each variant.

@@

    \paragraph{Experiment 3: Discount factor sensitivity.}
    In this experiment, we investigated the effect of $\gamma$ in the integrated agent's performance.
    We tested all $\gamma \in [0.8, 0.85, 0.9, 0.92, 0.94, 0.96, 0.98, 0.99, 1.0]$.
    As usual, all other hyper-parameters were kept frozen.
    To reduce the variance given the stochasticity, this experiment was performed 5 times for each variant.

    \paragraph{Experiment 4: Evaluation of different exploration strategies.}
    Following, we evaluated the impact of $10$ different $\epsilon$ decay curves.
    We assessed two types of curves: exponential decay functions, $\epsilon(t) = e^{-k t}$; and inverted logistic functions, $\epsilon(t) = 1 / (1 + e^{-k_{1} (t - k_{2})})$.
    Again, all other hyper-parameters were kept frozen.
    To reduce the variance given the stochasticity, this experiment was performed 10 times for each variant.
